---
title: "3D Print Analysis"
description: |
  This project examines the factors that can increase the strength and quality of a 3D print.
site: distill::distill_website
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# Learn more about creating websites with Distill at:
# https://rstudio.github.io/distill/website.html

# Learn more about publishing to GitHub Pages at:
# https://rstudio.github.io/distill/publish_website.html#github-pages

library(tidyverse)
library(dplyr)
library(knitr)
library(rmarkdown)
library(plotly)
library(bsselectR)
```

3D printing is one of the coolest high-tech products there is, and it's revolutionized our world.

So what actually makes a 3D print strong?

After examining the data, we found that each factor has its own unique effect on the strength and quality of the 3D print.

Currently, the best print uses:
* 0.06 mm Layer Height
* 5 mm Wall Thickness
* 90% Infill Density
* A Grid Infill Pattern
* 215°C Nozzle Temperature
* 95°C Bed Temperature
* 60 mm/s Print Speed
* PLA Filament
* And 75% Fan Speed

```{r pull_and_save, include = FALSE}
plots <- c(`Layer Height and Roughness` = "images/layer1.png",
           `Layer Height and Tension Strength` = "images/layer2.png",
           `Layer Height and Elongation` = "images/layer3.png",
           `Wall Thickness and Roughness` = "images/wall1.png",
           `Wall Thickness and Tension Strength` = "images/wall2.png",
           `Wall Thickness and Elongation` = "images/wall3.png",
           `Infill Density and Roughness` = "images/infilld1.png",
           `Infill Density and Tension Strength` = "images/infilld2.png",
           `Infill Density and Elongation` = "images/infilld3.png",
           `Infill Pattern and Roughness` = "images/infillp1.png",
           `Infill Pattern and Tension Strength` = "images/infillp2.png",
           `Infill Pattern and Elongation` = "images/infillp3.png",
           `Nozzle Temperature and Roughness` = "images/nozzle1.png",
           `Nozzle Temperature and Tension Strength` = "images/nozzle2.png",
           `Nozzle Temperature and Elongation` = "images/nozzle3.png",
           `Bed Temperature and Roughness` = "images/bed1.png",
           `Bed Temperature and Tension Strength` = "images/bed2.png",
           `Bed Temperature and Elongation` = "images/bed3.png",
           `Print Speed and Roughness` = "images/speedp1.png",
           `Print Speed and Tension Strength` = "images/speedp2.png",
           `Print Speed and Elongation` = "images/speedp3.png",
           `Material and Roughness` = "images/material1.png",
           `Material and Tension Strength` = "images/material2.png",
           `Material and Elongation` = "images/material3.png",
           `Fan Speed and Roughness` = "images/speedf1.png",
           `Fan Speed and Tension Strength` = "images/speedf2.png",
           `Fan Speed and Elongation` = "images/speedf3.png")
```


```{r, echo = FALSE}
bsselect(plots, type = "img", show_tick = TRUE, live_search = FALSE)
```

